%-------------------------
% Resume in Latex
% Author : Evgenii Koskelainen
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[8]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{#3} & #4 \\
      \textbf{#5} & #6 \\
      \textit{\small#7} & \textit{\small #8} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[3]{\resumeItem{#1}{#2}{#3}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Evgenii Koskelainen} & {Telegram}: \href{https://t.me/evgenii_kos/}{@evgenii\_kos}\\
  \textbf {Python developer, ML Engineer} & Linkedin: \href{https://www.linkedin.com/in/koskelainen/}{linkedin.com/in/koskelainen} \\
  \textbf & Email: \href{mailto:koskelainen8@gmail.com}{koskelainen8@gmail.com} \\
\end{tabular*}

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, SQL, HTML, Shell}
      \hfill
      \textbf{Technologies}{: Hadoop, Spark, gRPC, Kafka, Docker, OpenShift}

      \textbf{Python libs}{: PySpark, Pandas, NumPy, Scikit-learn, SciPy, XGboost, Shap}

      \textbf{DataBase}{: Oracle, PostgreSQL, ClickHouse, Redis}

    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sberbank}{Moscow, Russia}
      {Senior ML Engineer, Team Lead}{Sep. 2019 - Apr. 2022}
      \resumeItemListStart
        \resumeItem{EWS Model}
          {
Designed production model from MVP and data marts(Spark).
EWS(Early Warning System) model allows to capture risk indicators such as the probability of default and
financial, macroeconomic factors, and obtain a general assessment of credit deterioration.
Basically, it is multi models system that trains on big data with valuable insight.
}
        \resumeItem{Workflows}
          {
Designed the workflow framework MFW(Model’s FrameWork) to create and
manage model pipelines leveraging reusable patterns to expedite developer productivity.
The framework reduces the Time to Market each model by 15--25\%.
}
        \resumeItem{Management}
          {
Led the development of models, frameworks, DevOps, and integrations with other services.
}
      \resumeItemListEnd

    \resumeSubSubheading
     {Middle ML Engineer}{Dec. 2018 - Sep. 2019}
     \resumeItemListStart
        \resumeItem{NPL model and etc}
          {
Designed production models from MVP and data marts(Spark).
Models detect potentially Non-Performing Loans
where the likelihood of them being repaid in full is considered to be significantly lower.
}
        \resumeItem{Refactoring legacy}
          {
Refactored legacy models and redesigned with release to production.
}
     \resumeItemListEnd

    \resumeSubheading
      {OpenTechnologies}{Moscow, Russia}
      {Data Engineer}{Dec. 2017 - Dec. 2018}
      \resumeItemListStart
        \resumeItem{Geolocation Application}
          {
Refactored legacy backend module and developed ETL tools for a project.
Implemented module with process big data and integration with Splunk.
}
        \resumeItem{APM}
          {
Developed module to aggregate data from agent APM(Application Performance Management)
and a make general report about the system status.
}
      \resumeItemListEnd

    \resumeSubheading
      {Huawei Technologies}{St. Petersburg, Russia}
      {Python Developer}{May 2016 - Sep. 2017}
      \resumeItemListStart
        \resumeItem{Reporting}
          {
Developed an application for automatic report generation for KPIs achievement by region.
}
        \resumeItem{Monitoring system}
          {
Developed backed module to install and manage monitoring system icinga(nagios).
}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Bonch-Bruevich St. Petersburg State University of Telecommunications}\par
      \textbf{St. Petersburg, Russia}\par
      {Master of Secured Communications Systems}\hfill{Sep. 2003 -- June 2008}
    \resumeSubheading
      {The Bonch-Bruevich St. Petersburg State University of Telecommunications}\par
      \textbf{St. Petersburg, Russia}\par
      {Master of Economics and Managements to Communication}\hfill{Sep. 2006 -- June 2009}
  \resumeSubHeadingListEnd

\end{document}
